We are aiming to fully automate the process of scheduling and dispatching to become completely human-free with zero interference from humans whatsoever, and providing companies with a fully featured reporting capabilities that help them expands and grow bigger in no time.
	
\subsection{Machine Intelligence Techniques}
	We will implement machine intelligence algorithms and techniques that we've learned such as planing\cite{artificial_intelligence,} in order to fully automate the dispatching of tasks to technicians based on many parameters as:
	\begin{itemize}
		\item Technicians skills and reputation.
		\item Technicians previous jobs with the concerned customer.
		\item Technicians location when the job arrives.
		\item Spare-parts in technicians hands.
	\end{itemize}
	
	We aim to build a knowledge base for problems and spare parts to be able to assign the job and spare parts needed for it at the same time automatically rather than depend on technician to tell what are the spare parts needed for such problem.
	
	Also we will work on building a natural language processing module to be able to identify basic parts of problems and pass them to the ticketing system, this will allow customers to directly describe their problem through a web form and FSM will be able to identify and locate the problem and the needed skills to solve it.
	
\subsection{Data Science}
	We will implement data science techniques to get the most out of the data and wrap this information in a useful reporting module that will help companies generate dependable reports that can be used in making considerable business decisions, for example we'll implement association rules algorithms to know:
	\begin{itemize}
		\item Which areas that contains a higher rate of broken devices and need more technicians to cover.
		\item The most device that gets broken with what problem.
	\end{itemize}
	  